Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-18 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

While the finite-precision extension of the Kochen-Specker theorem
asserts the non-existence of a certain kind of QIVPMs, we also want
to understand what a QIVPM could be when it exists. In contrast with
the conventional Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}
and Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}:

@@

\noindent We haven't discussed how to construct a QIVPM according
to a simple rule. Even if we have a QIVPM, there might not have any
states consistent with it.

@@

In other words, if the measurement intervals are too imprecise and
the QIVPM are defined so wildly, the results we get might contradict
to each other, and exclude any possible state from being consistent
with the measurement results. To address this problem, we are going
to consider a simple rule which can induce well-behaved QIVPMs by
quantum probability measures systematically. Recall when we generalized
quantum probability measures to QIVPMs, we changed the range from
the unit interval~$\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
This replacement suggests us to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
which can be used to replace a real-valued probability~$\mu\left(P\right)$
by an interval-valued one~$\iota\left(\mu\left(P\right)\right)$.
In other words, compositing $\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
which has the same domain and range as a QIVPM. In order to guarantee
$\iota\circ\mu$ is always a QIVPM, we consider the following homomorphism-like
properties for $\iota$.

>>>>

A conventional quantum probability measure can be easily constructed
from a state according to Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
This state is also the unique state consistent with the constructed
probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}:

@@

\noindent Since QIVPMs are just finite precision generalization of
conventional quantum probability measures, we also want to seek a
simple rule to construct them, and understand which states are consistent
with the constructed QIVPM. However, there exists a QIVPM such that
no state can be consistent with it. Since no state is consistent with
it, there is no natural way to construct it from any state.

@@

In other words, if the measurement intervals are too imprecise and
the QIVPM are defined so wildly, the results we get might contradict
to each other, and exclude any possible state from being consistent
with the measurement results. To address this problem, we are going
to consider a simple rule which can induce well-behaved QIVPMs by
quantum probability measures systematically. Recall when we generalized
quantum probability measures to QIVPMs, we changed the range from
the unit interval~$\left[0,1\right]$ to a set of intervals~$\mathscr{I}$.
This replacement suggests to find a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
to replace a real-valued probability~$\mu\left(P\right)$ by an interval-valued
one~$\iota\left(\mu\left(P\right)\right)$. In other words, compositing
$\iota$ with a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
produces an interval-valued function~$\iota\circ\mu:\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$
which has the same domain and range as a QIVPM. In order to guarantee
$\iota\circ\mu$ always a QIVPM, we consider the following homomorphism-like
properties for $\iota$.
